{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-09 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref*{def:stepwise-wapg}. 

@@

        Recall the 
        \hyperref[prop:stepwise-lyapunov]{Proposition \ref*{prop:stepwise-lyapunov}}, 

>>>>

        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref{def:stepwise-wapg}. 

@@

        Recall Proposition \ref{prop:stepwise-lyapunov},
